How access to care shapes disease burden: the current impact of post-exposure prophylaxis and potential for expanded access to prevent human rabies deaths in Madagascar

### 2020-09-19 analysis/paper/manuscript.Rmd
fix names of functions

## data
ctar_metadata <- fread(here("data/processed/clinics/ctar_metadata.csv"))
district_bites <- fread(here("output/bites/district_bites.csv"))
mora_bites <- fread(here("output/bites/mora_bites.csv"))
mada_communes <- st_read(here("data/processed/shapefiles/mada_communes.shp"))
mada_districts <- st_read(here("data/processed/shapefiles/mada_districts.shp"))

## All preds (for abstract stats etc)
natl_preds <- fread(here("output/preds/natl_preds.gz"))
natl_base <- natl_preds[scenario == 0]

@@

admin_base <- fread(here("output/preds/admin_preds_base.gz"))

## candidate points
csbs <- fread(here("data/processed/clinics/csb2.csv"))
clin_per_comm <- fread(here("data/processed/clinics/clinic_per_comm.csv"))
clin_per_dist <- fread(here("data/processed/clinics/clinic_per_dist.csv"))
missing_comms <- fread(here("output/stats/missing_comms.csv"))
comms_no_clins <- nrow(mada_communes) - (nrow(clin_per_comm) + nrow(ctar_metadata) + nrow(clin_per_dist))
csbs_max <- rbind(csbs, clin_per_comm[!(clinic_id %in% csbs$clinic_id)], fill = TRUE)

max_added <- max(natl_preds$scenario)
natl_preds %>%
  group_by(scale, data_source) %>%
  arrange(scenario) %>%
  mutate_at(vars(-c(group_cols(), scenario)), function(x) x/x[1]) -> props
trends <- read.csv(here("output/stats/trends_adminpreds.csv"))

@@

```{r fig 1}
include_graphics(here("figs/main/M1_sankey.jpeg"))
```

@@

## Estimating travel times to the closest ARMC {#results-ttimes}
```{r ttime stats}
ttime_stats <- read.csv(here("output/stats/prop_pop_ttimes.csv"))
# get prop of pop > 3 hrs away at baseline
ttime_stats %>%
  filter(scenario == 0, !(cut_times %in% c("0-1", "1-2", "2-3"))) %$%
  sum(prop_pop) -> prop_over3_base
ttime_stats %>%
  filter(scenario == 0, !(cut_times %in% c("0-1", "1-2", "2-3", "4-5", "5-6"))) %$%
  sum(prop_pop) -> prop_over6_base
```

@@

```{r fig M2}
include_graphics(here("figs/main/M2_ttimes.jpeg"))
```

@@

```{r fig M3 catchmaps}
include_graphics(here("figs/main/M3_bitemaps.jpeg"))
```

@@

```{r fig M4 biteinc}
include_graphics(here("figs/main/M4_biteinc.jpeg"))
```

@@

```{r}
outliers <- read.csv(here("output/stats/outliers.csv"))
```

@@

## Modeling reported bite incidence as a function of travel times {#results-bitemods}
```{r}
convergence <- read.csv(here("output/stats/convergence.csv"))
```

@@

```{r fig 5}
include_graphics(here("figs/main/M5_mods.jpeg"))
```

@@

```{r fig 6}
include_graphics(here("figs/main/M6_burden_base.jpeg"))
```

@@

```{r fig 7}
include_graphics(here("figs/main/M7_addARMC.jpeg"))
```

@@

## Box 1: case studies of the challenges of predicting health seeking behavior and PEP efficacy
```{r}
mora_bites %>%
  filter(district == "Anosibe-An'ala") %>%
  summarize(pop = sum(pop, na.rm = TRUE), bites = sum(avg_bites, na.rm = TRUE), 
            inc = bites/pop*1e5) -> aa_bites
mora_raw <- read.csv(here("data/processed/bitedata/moramanga.csv"))
mora_raw %>%
  filter(distcode == "MG33317") %>%
  summarize(prop_cat1 = sum(known_cat1)/n()) -> prop_cat1_AA
admin_preds <- fread(here("output/preds/admin_preds_base.gz")) 
admin_preds %>%
  mutate(distcode = substr(names, 1, 7)) %>%
  filter(distcode == "MG33317") %>%
  group_by(scale) %>%
  summarize(inc = sum(deaths_mean)/sum(pop)*1e5, bite_inc = sum(bites_mean)/sum(pop)*1e5) -> aa_preds

ranked_clins <- fread(here("output/ttimes/addclinics/clinics_ranked.csv"))
aa_added <- min(ranked_clins[district == "Anosibe-An'ala"]$scenario)
gtruth <- fread(here("output/ttimes/gtruth_ttimes.csv"))
gtruth %>%
  filter(district == "Anosibe-An'ala") %>%
  summarize(mean = mean(ttimes_reported, na.rm = TRUE), 
            min =  min(ttimes_reported, na.rm = TRUE),
            max = max(ttimes_reported, na.rm = TRUE)) -> aa_ttimes
admin_base %>%
  mutate(distcode = substr(names, 1, 7)) %>%
  filter(distcode == "MG33317") %>%
  group_by(scale) %>%
  summarize(deaths_mean = sum(deaths_mean), pop = sum(pop)) -> aa_deaths

@@

```{r}
catch_trends <- fread(here("output/stats/trend_catches.csv"))
catch_trends %>% 
  group_by(scenario) %>% 
  summarize(mean_pops = mean(pops_mean)) %>%
  as.data.table() -> catch_pops
```

@@

```{r fig S1.1 inputs A friction B pop}
include_graphics(here("figs/supplementary/S1.1_inputs.jpeg"))
```

@@

```{r fig S1.2 ttimes A Moramanga B Drive}
include_graphics(here("figs/supplementary/S1.2_raw.jpeg"))
```

@@

```{r fig S1.3 travel modes}
include_graphics(here("figs/supplementary/S1.3_modes.jpeg"))
```

@@

```{r fig S1.4 lms ttimes}
include_graphics(here("figs/supplementary/S1.4_lms.jpeg"))
```

@@

*__[Table S1.1.]{#tabS1.1}__ R^2^ values from linear models with estimated access metrics predicting either driving times or commune means of patient reported travel times.*
```{r table S1.1 lms table}
S1.1_table <- read.csv(here("output/stats/access_met_r2.csv"), row.names = 1)
kable(S1.1_table, col.names = c("Predictor", "Driving times", 
                                "Commune mean of patient reported travel times"))
```

```{r fig S1.5 output ttimes A district B commune}
include_graphics(here("figs/supplementary/S1.5_outputs.jpeg"))
```

@@

```{r fig S2.1 A catchments B closest C Prop bites}
include_graphics(here("figs/supplementary/S2.1_catchments.jpeg"))
```

@@

```{r fig 2.2 form sub A time series B reporting C vial comp}
include_graphics(here("figs/supplementary/S2.2_vialcomps.jpeg"))
```

@@

```{r fig S3.1 corr pop ttimes}
include_graphics(here("figs/supplementary/S3.1_corrs.jpeg"))
```
_**Figure S3.1.** Correlation between travel time in hours (the average weighted by the population) and population size of administrative units at the district and commune scale._\

@@

*__Table S3.1.__ DIC Estimates for all models. Models with the lowest DIC for each dataset and scale of covariate are in bold.  For the column pop effect, addPop = models with population size as additional covariate, onlyPop = models with population as only covariate, flatPop = models with population as offset in model. For the intercept type: random = random intercept by catchment, fixed = a single fixed intercept was estimated).*
```{r table S3.1 dic}
model_ests <- read.csv(here("output/mods/estimates.csv"))
model_ests %>%
  filter(OD == FALSE) %>%
  select(params, Mean, pop_predict, intercept, data_source, scale) %>%
  spread(key = params, value = Mean, fill = 0) -> model_means
model_ests %>%
  group_by(data_source, scale, pop_predict, intercept) %>%
  summarize(dic = mean(dic)) -> dic_ests
dic_ests %>%
  group_by(data_source) %>%
  arrange(dic, .by_group = TRUE) %>%
  mutate(dic = round(dic, 2)) -> dic_ranks
knitr::kable(dic_ranks, 
             col.names = c("Dataset", "Scale", "Pop effect", "Intercept type", "DIC"))
```
<br/>

```{r fig S3.2 obs vs predicted}
include_graphics(here("figs/supplementary/S3.2_fitted.jpeg"))
```

@@

```{r fig S3.3 out of fit}
include_graphics(here("figs/supplementary/S3.3_outfit.jpeg"))
```

@@

```{r fig S3.4 od comp posts}
include_graphics(here("figs/supplementary/S3.4_posts_all.jpeg"))
```

@@

```{r fig S3.5 od comp preds}
include_graphics(here("figs/supplementary/S3.5_preds_OD.jpeg"))
```

@@

```{r fig S3.6 random vs od}
include_graphics(here("figs/supplementary/S3.6_posts_intercepts.jpeg"))
```

@@

```{r fig S3.7 random vs od}
include_graphics(here("figs/supplementary/S3.7_preds_ODcomp.jpeg"))
```

@@

```{r fig S3.8 rep cutoff posts}
include_graphics(here("figs/supplementary/S3.8_posts_rep_se.jpeg"))
```

@@

```{r fig S3.9 rep cutoff preds}
include_graphics(here("figs/supplementary/S3.9_preds_rep_se.jpeg"))
```

@@

```{r fig S4.1 exp range}
include_graphics(here("figs/supplementary/S4.1_exprange.jpeg"))
```

@@

```{r fig S5.1 metrics}
include_graphics(here("figs/supplementary/S5.1_tests.jpeg"))
```
_**Figure S5.1.** Comparing metrics for ranking clinics for targeted expansion to 83 additional districts (so that each district has an ARMC). We simulated expansion using three different ranking metrics: 1) reduction in mean travel times (green line) 2) the proportion of the population for which travel times were reduced (red dashed line) and 3) the proportion of the population for which travel times were reduced weighted by the reduction in travel times (pink dashed line). For each of these, we simulated burden using our decision tree framework (y axis is the mean of 1000 simulations of annual deaths at the national level). The blue lines show 10 simulations of randomly expanding access on reducing burden as a comparator. The panels show to the commune and district model of reported bite incidence. _

```{r fig S5.2 add clinics}
include_graphics(here("figs/supplementary/S5.2_ARMCadded.jpeg"))
```
_**Figure S5.2.** Map of the location and at what step each clinic was added. The circles are each of the CSB II across the country sized by the resulting average reduction in burden (based on smoothed annual burden estimates from the commune model, see inset). The large white crosses show the location of the existing 31 ARMC in Madagascar and the smaller white crosses are the additional CSB II in the country which were added in the final step but not ranked._

```{r fig S5.3 map shifts}
include_graphics(here("figs/supplementary/S5.3_map_shifts.jpeg"))
```
_**Figure S5.3.** Maps of how travel times change as clinics are added at the **A)** ~1 x 1 km grid cell **B)** commune and **C)** district scales. The columns are ordered by the number or clinics at each step: baseline (N = 31), + 83 (1 per district), + 200, + 600, + 1406 (1 per commune), and max (+ 1696 clinics, all additional CSB IIs in the country). Grey pixels show the location of ARMC at each step. Commune and district values are the average grid cell travel times weighted by the population in each cell._

```{r fig S5.4 travel times(a) bite inc(b)}
include_graphics(here("figs/supplementary/S5.4_ttimes_bites.jpeg"))
```
_**Figure S5.4.** Shifts in estimated **A)** travel times (hrs, x-axis is square root transformed), **B)** bite incidence per 100,000 persons and boxplots showing the median for communes and district models (colors) as clinics are added._

```{r fig S5.5 reporting(a) death inc(b)}
include_graphics(here("figs/supplementary/S5.5_reporting_shifts.jpeg"))
```
_**Figure S5.5.** Shifts in estimated **A)** reporting, **B)** death incidence per 100,000 persons for the commune and district models (colors) as clinics are added._

```{r fig S5.6 catch(a) vials(b) throughput(c)}
include_graphics(here("figs/supplementary/S5.6_clinic_shifts.jpeg"))
```
_**Figure S5.6.** Shifts in average clinic **A)** catchment population size, **B)** annual vial demand, and **C)** daily throughput (i.e. average number of patients reporting each day) given estimates of bite incidence for the commune and district models (colors). For vial demand estimation, catchment population sizes are the same for each model as these populations are allocated at the grid cell level (i.e. population in a grid cell is allocated to the clinic catchment it is closest to in terms of travel times regardless of district or commune). All x-axes are log transformed._

```{r fig S5.7 comm network}
include_graphics(here("figs/supplementary/S5.7_comm_map.jpeg"))
```

@@

```{r fig S5.8 dist network}
include_graphics(here("figs/supplementary/S5.8_dist_map.jpeg"))
```

@@

```{r se tables}
se_pars <- read.csv(here("output/sensitivity/se_pars.csv"))

@@

```{r fig S6.1 base se}
include_graphics(here("figs/supplementary/S6.1_base_se.jpeg"))
```

@@

```{r fig S6.2 add se}
include_graphics(here("figs/supplementary/S6.2_addARMC_se.jpeg"))
```

@@

```{r fig S6.3 vial se}
include_graphics(here("figs/supplementary/S6.3_vial_se.jpeg"))
```

@@

```{r fig S6.4 scaling factors}
include_graphics(here("figs/supplementary/S6.4_scaling_rels.jpeg"))
```

@@

```{r fig S6.5 scaling se}
include_graphics(here("figs/supplementary/S6.5_scaling_se.jpeg"))
```

>>>>

## data
ctar_metadata <- fread(here("data-raw/out/clinics/ctar_metadata.csv"))
district_bites <- fread(here("analysis/out/bites/district_bites.csv"))
mora_bites <- fread(here("analysis/out/bites/mora_bites.csv"))
mada_communes <- st_read(here("analysis/out/shapefiles/mada_communes.shp"))
mada_districts <- st_read(here("analysis/out/shapefiles/mada_districts.shp"))

## All preds (for abstract stats etc)
natl_preds <- fread(here("analysis/out/preds/natl_preds.gz"))
natl_base <- natl_preds[scenario == 0]

@@

admin_base <- fread(here("analysis/out/preds/admin_preds_base.gz"))

## candidate points
csbs <- fread(here("data-raw/out/clinics/csb2.csv"))
clin_per_comm <- fread(here("data-raw/out/clinics/clinic_per_comm.csv"))
clin_per_dist <- fread(here("data-raw/out/clinics/clinic_per_dist.csv"))
missing_comms <- fread(here("analysis/out/stats/missing_comms.csv"))
comms_no_clins <- nrow(mada_communes) - (nrow(clin_per_comm) + nrow(ctar_metadata) + nrow(clin_per_dist))
csbs_max <- rbind(csbs, clin_per_comm[!(clinic_id %in% csbs$clinic_id)], fill = TRUE)

max_added <- max(natl_preds$scenario)
natl_preds %>%
  group_by(scale, data_source) %>%
  arrange(scenario) %>%
  mutate_at(vars(-c(group_cols(), scenario)), function(x) x/x[1]) -> props
trends <- read.csv(here("analysis/out/stats/trends_adminpreds.csv"))

@@

```{r fig 1}
include_graphics(here("analysis/figs/main/M1_sankey.jpeg"))
```

@@

## Estimating travel times to the closest ARMC {#results-ttimes}
```{r ttime stats}
ttime_stats <- read.csv(here("analysis/out/stats/prop_pop_ttimes.csv"))
# get prop of pop > 3 hrs away at baseline
ttime_stats %>%
  filter(scenario == 0, !(cut_times %in% c("0-1", "1-2", "2-3"))) %$%
  sum(prop_pop) -> prop_over3_base
ttime_stats %>%
  filter(scenario == 0, !(cut_times %in% c("0-1", "1-2", "2-3", "4-5", "5-6"))) %$%
  sum(prop_pop) -> prop_over6_base
```

@@

```{r fig M2}
include_graphics(here("analysis/figs/main/M2_ttimes.jpeg"))
```

@@

```{r fig M3 catchmaps}
include_graphics(here("analysis/figs/main/M3_bitemaps.jpeg"))
```

@@

```{r fig M4 biteinc}
include_graphics(here("analysis/figs/main/M4_biteinc.jpeg"))
```

@@

```{r}
outliers <- read.csv(here("analysis/out/stats/outliers.csv"))
```

@@

## Modeling reported bite incidence as a function of travel times {#results-bitemods}
```{r}
convergence <- read.csv(here("analysis/out/stats/convergence.csv"))
```

@@

```{r fig 5}
include_graphics(here("analysis/figs/main/M5_mods.jpeg"))
```

@@

```{r fig 6}
include_graphics(here("analysis/figs/main/M6_burden_base.jpeg"))
```

@@

```{r fig 7}
include_graphics(here("analysis/figs/main/M7_addARMC.jpeg"))
```

@@

## Box 1: case studies of the challenges of predicting health seeking behavior and PEP efficacy
```{r}
mora_bites %>%
  filter(district == "Anosibe-An'ala") %>%
  summarize(pop = sum(pop, na.rm = TRUE), bites = sum(avg_bites, na.rm = TRUE), 
            inc = bites/pop*1e5) -> aa_bites
mora_raw <- read.csv(here("data-raw/out/bitedata/moramanga.csv"))
mora_raw %>%
  filter(distcode == "MG33317") %>%
  summarize(prop_cat1 = sum(known_cat1)/n()) -> prop_cat1_AA
admin_preds <- fread(here("analysis/out/preds/admin_preds_base.gz")) 
admin_preds %>%
  mutate(distcode = substr(names, 1, 7)) %>%
  filter(distcode == "MG33317") %>%
  group_by(scale) %>%
  summarize(inc = sum(deaths_mean)/sum(pop)*1e5, bite_inc = sum(bites_mean)/sum(pop)*1e5) -> aa_preds

ranked_clins <- fread(here("analysis/out/ttimes/addclinics/clinics_ranked.csv"))
aa_added <- min(ranked_clins[district == "Anosibe-An'ala"]$scenario)
gtruth <- fread(here("analysis/out/ttimes/gtruth_ttimes.csv"))
gtruth %>%
  filter(district == "Anosibe-An'ala") %>%
  summarize(mean = mean(ttimes_reported, na.rm = TRUE), 
            min =  min(ttimes_reported, na.rm = TRUE),
            max = max(ttimes_reported, na.rm = TRUE)) -> aa_ttimes
admin_base %>%
  mutate(distcode = substr(names, 1, 7)) %>%
  filter(distcode == "MG33317") %>%
  group_by(scale) %>%
  summarize(deaths_mean = sum(deaths_mean), pop = sum(pop)) -> aa_deaths

@@

```{r}
catch_trends <- fread(here("analysis/out/stats/trend_catches.csv"))
catch_trends %>% 
  group_by(scenario) %>% 
  summarize(mean_pops = mean(pops_mean)) %>%
  as.data.table() -> catch_pops
```

@@

```{r fig S1.1 inputs A friction B pop}
include_graphics(here("analysis/figs/supplementary/S1.1_inputs.jpeg"))
```

@@

```{r fig S1.2 ttimes A Moramanga B Drive}
include_graphics(here("analysis/figs/supplementary/S1.2_raw.jpeg"))
```

@@

```{r fig S1.3 travel modes}
include_graphics(here("analysis/figs/supplementary/S1.3_modes.jpeg"))
```

@@

```{r fig S1.4 lms ttimes}
include_graphics(here("analysis/figs/supplementary/S1.4_lms.jpeg"))
```

@@

*__[Table S1.1.]{#tabS1.1}__ R^2^ values from linear models with estimated access metrics predicting either driving times or commune means of patient reported travel times.*
```{r table S1.1 lms table}
S1.1_table <- read.csv(here("analysis/out/stats/access_met_r2.csv"), row.names = 1)
kable(S1.1_table, col.names = c("Predictor", "Driving times", 
                                "Commune mean of patient reported travel times"))
```

```{r fig S1.5 output ttimes A district B commune}
include_graphics(here("analysis/figs/supplementary/S1.5_outputs.jpeg"))
```

@@

```{r fig S2.1 A catchments B closest C Prop bites}
include_graphics(here("analysis/figs/supplementary/S2.1_catchments.jpeg"))
```

@@

```{r fig 2.2 form sub A time series B reporting C vial comp}
include_graphics(here("analysis/figs/supplementary/S2.2_vialcomps.jpeg"))
```

@@

```{r fig S3.1 corr pop ttimes}
include_graphics(here("analysis/figs/supplementary/S3.1_corrs.jpeg"))
```
_**Figure S3.1.** Correlation between travel time in hours (the average weighted by the population) and population size of administrative units at the district and commune scale._\

@@

*__Table S3.1.__ DIC Estimates for all models. Models with the lowest DIC for each dataset and scale of covariate are in bold.  For the column pop effect, addPop = models with population size as additional covariate, onlyPop = models with population as only covariate, flatPop = models with population as offset in model. For the intercept type: random = random intercept by catchment, fixed = a single fixed intercept was estimated).*
```{r table S3.1 dic}
model_ests <- read.csv(here("analysis/out/mods/estimates.csv"))
model_ests %>%
  filter(OD == FALSE) %>%
  select(params, Mean, pop_predict, intercept, data_source, scale) %>%
  spread(key = params, value = Mean, fill = 0) -> model_means
model_ests %>%
  group_by(data_source, scale, pop_predict, intercept) %>%
  summarize(dic = mean(dic)) -> dic_ests
dic_ests %>%
  group_by(data_source) %>%
  arrange(dic, .by_group = TRUE) %>%
  mutate(dic = round(dic, 2)) -> dic_ranks
knitr::kable(dic_ranks, 
             col.names = c("Dataset", "Scale", "Pop effect", "Intercept type", "DIC"))
```
<br/>

```{r fig S3.2 obs vs predicted}
include_graphics(here("analysis/figs/supplementary/S3.2_fitted.jpeg"))
```

@@

```{r fig S3.3 out of fit}
include_graphics(here("analysis/figs/supplementary/S3.3_outfit.jpeg"))
```

@@

```{r fig S3.4 od comp posts}
include_graphics(here("analysis/figs/supplementary/S3.4_posts_all.jpeg"))
```

@@

```{r fig S3.5 od comp preds}
include_graphics(here("analysis/figs/supplementary/S3.5_preds_OD.jpeg"))
```

@@

```{r fig S3.6 random vs od}
include_graphics(here("analysis/figs/supplementary/S3.6_posts_intercepts.jpeg"))
```

@@

```{r fig S3.7 random vs od}
include_graphics(here("analysis/figs/supplementary/S3.7_preds_ODcomp.jpeg"))
```

@@

```{r fig S3.8 rep cutoff posts}
include_graphics(here("analysis/figs/supplementary/S3.8_posts_rep_se.jpeg"))
```

@@

```{r fig S3.9 rep cutoff preds}
include_graphics(here("analysis/figs/supplementary/S3.9_preds_rep_se.jpeg"))
```

@@

```{r fig S4.1 exp range}
include_graphics(here("analysis/figs/supplementary/S4.1_exprange.jpeg"))
```

@@

```{r fig S5.1 metrics}
include_graphics(here("analysis/figs/supplementary/S5.1_tests.jpeg"))
```
_**Figure S5.1.** Comparing metrics for ranking clinics for targeted expansion to 83 additional districts (so that each district has an ARMC). We simulated expansion using three different ranking metrics: 1) reduction in mean travel times (green line) 2) the proportion of the population for which travel times were reduced (red dashed line) and 3) the proportion of the population for which travel times were reduced weighted by the reduction in travel times (pink dashed line). For each of these, we simulated burden using our decision tree framework (y axis is the mean of 1000 simulations of annual deaths at the national level). The blue lines show 10 simulations of randomly expanding access on reducing burden as a comparator. The panels show to the commune and district model of reported bite incidence. _

```{r fig S5.2 add clinics}
include_graphics(here("analysis/figs/supplementary/S5.2_ARMCadded.jpeg"))
```
_**Figure S5.2.** Map of the location and at what step each clinic was added. The circles are each of the CSB II across the country sized by the resulting average reduction in burden (based on smoothed annual burden estimates from the commune model, see inset). The large white crosses show the location of the existing 31 ARMC in Madagascar and the smaller white crosses are the additional CSB II in the country which were added in the final step but not ranked._

```{r fig S5.3 map shifts}
include_graphics(here("analysis/figs/supplementary/S5.3_map_shifts.jpeg"))
```
_**Figure S5.3.** Maps of how travel times change as clinics are added at the **A)** ~1 x 1 km grid cell **B)** commune and **C)** district scales. The columns are ordered by the number or clinics at each step: baseline (N = 31), + 83 (1 per district), + 200, + 600, + 1406 (1 per commune), and max (+ 1696 clinics, all additional CSB IIs in the country). Grey pixels show the location of ARMC at each step. Commune and district values are the average grid cell travel times weighted by the population in each cell._

```{r fig S5.4 travel times(a) bite inc(b)}
include_graphics(here("analysis/figs/supplementary/S5.4_ttimes_bites.jpeg"))
```
_**Figure S5.4.** Shifts in estimated **A)** travel times (hrs, x-axis is square root transformed), **B)** bite incidence per 100,000 persons and boxplots showing the median for communes and district models (colors) as clinics are added._

```{r fig S5.5 reporting(a) death inc(b)}
include_graphics(here("analysis/figs/supplementary/S5.5_reporting_shifts.jpeg"))
```
_**Figure S5.5.** Shifts in estimated **A)** reporting, **B)** death incidence per 100,000 persons for the commune and district models (colors) as clinics are added._

```{r fig S5.6 catch(a) vials(b) throughput(c)}
include_graphics(here("analysis/figs/supplementary/S5.6_clinic_shifts.jpeg"))
```
_**Figure S5.6.** Shifts in average clinic **A)** catchment population size, **B)** annual vial demand, and **C)** daily throughput (i.e. average number of patients reporting each day) given estimates of bite incidence for the commune and district models (colors). For vial demand estimation, catchment population sizes are the same for each model as these populations are allocated at the grid cell level (i.e. population in a grid cell is allocated to the clinic catchment it is closest to in terms of travel times regardless of district or commune). All x-axes are log transformed._

```{r fig S5.7 comm network}
include_graphics(here("analysis/figs/supplementary/S5.7_comm_map.jpeg"))
```

@@

```{r fig S5.8 dist network}
include_graphics(here("analysis/figs/supplementary/S5.8_dist_map.jpeg"))
```

@@

```{r se tables}
se_pars <- read.csv(here("analysis/out/sensitivity/se_pars.csv"))

@@

```{r fig S6.1 base se}
include_graphics(here("analysis/figs/supplementary/S6.1_base_se.jpeg"))
```

@@

```{r fig S6.2 add se}
include_graphics(here("analysis/figs/supplementary/S6.2_addARMC_se.jpeg"))
```

@@

```{r fig S6.3 vial se}
include_graphics(here("analysis/figs/supplementary/S6.3_vial_se.jpeg"))
```

@@

```{r fig S6.4 scaling factors}
include_graphics(here("analysis/figs/supplementary/S6.4_scaling_rels.jpeg"))
```

@@

```{r fig S6.5 scaling se}
include_graphics(here("analysis/figs/supplementary/S6.5_scaling_se.jpeg"))
```
